\vspace{-2cm}Formation Control of AAUSHIP

### 2015-04-11 paper.tex
texttt

The rigid body forces are written as:
\begin{align}
M_{RB} \dot \nu_r + C_{RB}(\nu_r)\nu_r = \tau_{RB}
\label{eq:rigidmodel}
\end{align}
where
\begin{align}
M_{RB} &\text{ is the system inertia matrix}\nonumber\\
C_{RB} &\text{ is coriolis-centriopedal matrix}\nonumber\\
\tau_{RB} &\text{ is a lumped force combined of } \tau_{\text{hyd}} + \tau_{\text{hs}} + \tau_{\text{wind}} + \tau_{\text{wave}}\nonumber
\end{align}
where in $\tau_{RB}$
\begin{align}
\qquad \tau_{\text{hyd}} &\text{ is the hydrodynamic force}\nonumber\\
\qquad \tau_{\text{hs}} &\text{ is the hydrostatic force}\nonumber\\
\qquad \tau_{\text{wind}} &\text{ is the wind force}\nonumber\\
\qquad \tau_{\text{wave}} &\text{ is the wave force}\nonumber
\end{align}

@@

Here the first solution is applied where the two agents, that were too
close to each other, have been clustered into one, seen from the
$i$'th agent. Now the local minima between the agents have been
neglected and the $i$'th agent can generate its trajectory around the
agents and continue to the endpoint of the potential field. The
algorithm checks if the distances between the agents are lower that $2
\cdot r$. If this is the case it means that the $i$'th agent cannot
generate a trajectory in between these agents, which can lead to a
local minima. Therefore is the agents that are too close combined into
one by generating the middle point between their positions and
generating a new radius. This makes a larger circle where the two
agents are in the subset. This circle will be larger depending on the
wanted safety radius thus rises the need to recheck the potential
field again after have generated a new combined agent. If the radius
of the new agent places it close to one of the single agents, these
also might need to cluster. Thus the algorithm needs to run until no
distances between agents are $< 2 \cdot r$.

@@

potfield.m, pathgen.m, shipcontroller.m, simaauship.m, simaauship2.m.

The potfield.m is the potential field algorithm, where the magnitudes
of the field is generated. The pathgen.m is the trajectory generation,
which takes in a set of waypoints and generates the line segments that
the vessels needs to follow. The controller applied at the AAUSHIP is
a heading controller, which is handled in the shipcontroller.m. To
simulate the AAUSHIP is two files used; simaauship.m and
simaauship2.m. The first is used to simulate the individual vessel and
verify the dynamics of a single ship, and the latter is for simulating
the formation with the potfield.m and pathgen.m applied.

>>>>

The rigid body forces are written as:
\begin{align}
M_{RB} \dot \nu_r + C_{RB}(\nu_r)\nu_r = \tau_{RB}
\label{eq:rigidmodel}
\end{align}
where
\begin{align}
M_{RB} &\text{ is the system inertia matrix}\nonumber\\
C_{RB} &\text{ is coriolis-centriopedal matrix}\nonumber\\
\tau_{RB} &\text{ is a lumped force combined of } \tau_{\text{hyd}} + \tau_{\text{hs}} + \tau_{\text{wind}} + \tau_{\text{wave}}\nonumber
\end{align}
where in $\tau_{RB}$
\begin{align}
\tau_{\text{hyd}} &\text{ is the hydrodynamic force}\nonumber\\
\tau_{\text{hs}} &\text{ is the hydrostatic force}\nonumber\\
\tau_{\text{wind}} &\text{ is the wind force}\nonumber\\
\tau_{\text{wave}} &\text{ is the wave force}\nonumber
\end{align}

@@

Here the first solution is applied where the two agents, that were too
close to each other, have been clustered into one, seen from the
$i$'th agent. Now the local minima between the agents have been
neglected and the $i$'th agent can generate its trajectory around the
agents and continue to the endpoint of the potential field. The
algorithm checks if the distances between the agents are lower that $2
\cdot r$. If this is the case it means that the $i$'th agent cannot
generate a trajectory in between these agents, which can lead to a
local minima. Therefore is the agents that are too close combined into
one by generating the middle point between their positions and
generating a new radius. This makes a larger circle where the two
agents are in the subset. This circle will be larger depending on the
wanted safety radius thus rises the need to recheck the potential
field again after have generated a new combined agent. If the radius
of the new agent places it close to one of the single agents, these
also might need to cluster. Thus the algorithm needs to run until no
distances between agents are less than two times the radius.

@@

{\footnotesize
\texttt{potfield.m}, \texttt{pathgen.m}, \texttt{shipcontroller.m},\\
\texttt{simaauship.m}, \texttt{simaauship2.m}.
}

The \texttt{potfield.m} is the potential field algorithm, where the magnitudes
of the field is generated. The pathgen.m is the trajectory generation,
which takes in a set of waypoints and generates the line segments that
the vessels needs to follow. The controller applied at the AAUSHIP is
a heading controller, which is handled in the shipcontroller.m. To
simulate the AAUSHIP is two files used; simaauship.m and
simaauship2.m. The first is used to simulate the individual vessel and
verify the dynamics of a single ship, and the latter is for simulating
the formation with the \texttt{potfield.m} and \texttt{pathgen.m} applied.
